Variation in Primary Care Prescribing in Wales due to COVID-19

### 2021-03-05 writing/paper.Rmd
Removed LPA section from paper

* We did not assume that the existing processes would be the same for all drugs or all GP practices, therefore, we investigated the fit of several different time series models to the pre-COVID data. 
* We used the `fable` [@R-fable], `fasster` [@R-fasster], and the `fable.prophet` [@R-fable.prophet] packages to conduct the time series analyses.
  * Time series linear model
  * Decomposition model
  * Seasonal naïve (with and without drift)
  * Autoregressive integrated moving average [ARIMA; @Box2015]
  * Holt-Winters Additive Model [@Chatfield1978]
  * Prophet [@Taylor2018]
  * Combination models [cf. @Thomson2019]
* Prescribing quantities log transformed and forecasts use median values to reduce bias that back transformation would introduce when using the mean
* Using Jan 2015 to Feb 2020 data, we fitted several different models and assessed their accuracy using a cross-validated process to reduce the likelihood of overfitting models to the data.
  * Started with 36 months of data, used 6-month horizon as this was the horizon we would be using for the forecasts, 3-month step (to reduce computation time) **Do we want to re-run this with 1-month?**
    * Only interested in one forecast horizon: six-months

@@

## Identifying different prescribing behaviours - LPA

* What is LPA
  * Differences from clustering methods (e.g., k-means and hierarchical)

When conducting LPA, several models are specified and then evaluated. Model selection, including class enumeration, should not be based solely on statistical criteria, but also the statistical adequacy and substantive meaning of the solutions [@Marsh2009; @Morin2016]. Indeed, relying solely on statistical criteria in large samples may lead to the inability to identify an "optimal solution" as model fit increases as the number of classes increase [@Morin2009].

In this study we inspected the Bayesian Information Criterion [BIC; @Schwartz1978] and the bootstrapped likelihood ratio test [BLRT; @McLachlan2000] during the class enumeration process as the results of Monte-Carlo simulation study [@Nylund2007] showed them outperform other information criteria and likelihood-based tests.

* Entropy
* Posterior probabilities

@@

### All drugs

>>>>

* We did not assume that the existing processes would be the same for all drugs or all GP practices, therefore, we investigated the fit of several different time series models to the pre-COVID data. 
* We used the `fable` [@R-fable], `fasster` [@R-fasster], and the `fable.prophet` [@R-fable.prophet] packages to conduct the time series analyses.
  * Time series linear model
  * Decomposition model
  * Seasonal naïve (with and without drift)
  * Autoregressive integrated moving average [ARIMA; @Box2015]
  * Holt-Winters Additive Model [@Chatfield1978]
  * Prophet [@Taylor2018]
  * Combination models [cf. @Thomson2019]
* Prescribing quantities log transformed and forecasts use median values to reduce bias that back transformation would introduce when using the mean
* Using Jan 2015 to Dec 2019 data, we fitted several different models and assessed their accuracy using a cross-validated process to reduce the likelihood of overfitting models to the data.
  * Started with 36 months of data, used 6-month horizon as this was the horizon we would be using for the forecasts, 3-month step (to reduce computation time) **Do we want to re-run this with 1-month?**
    * Only interested in one forecast horizon: six-months

@@

@@

### All prescribing
